\papertitle

### 2021-05-31 source_separation/paper/paper.tex
Add justification for target creation process
Edit description of Eq.1

		\begin{enumerate}
			\item Static sounds that do not change harmonically over time
			\item Sounds in which there is at least some pitched content and not only noise
		\end{enumerate}			
		The sounds chosen include alarms, bells, engine noises, soundscapes, synthesizer chords, and sound effects. Each target that we used for testing was a combination of four randomly chosen source sounds from the group of 90 sounds. 
		When a target is created, the longest of the four sources is chosen to start playing at the beginning of the target. The other three sources are then randomly assigned different times to begin playing such that they will start between the beginning of the target and half-way through the longest source sound.

@@

		The distance metric cuts the target and solution into successive frames that are 4,000 samples in length, which is approximately 90 milliseconds at a sampling rate of 44.1 kHz. The spectral distance, as defined in Eqn. \ref{eqn:distance}, is calculated between corresponding frames of the target and solution. The spectral distance metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization, and used in \cite{Cella2020b} to compare accuracies of orchestrations. The equation takes in the FFT of the target $x$ and FFT of the solution $\tilde{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways. For our purposes, we used $\lambda_1 = 0.5$ and $\lambda_2 = 10$, which penalizes a solution that overshoots the harmonic energy of the target.

>>>>

		\begin{enumerate}
			\item Static sounds that do not change harmonically over time
			\item Sounds in which there is at least some pitched content and not only noise
		\end{enumerate}			
		The sounds chosen include alarms, bells, engine noises, soundscapes, synthesizer chords, and sound effects. Each target that we used for testing was a combination of four randomly chosen source sounds from the group of 90 sounds. 
		When a target is created, the longest of the four sources is chosen to start playing at the beginning of the target. The other three sources are then randomly assigned different times to begin playing such that they will start between the beginning of the target and half-way through the longest source sound. This is done to ensure that the sources overlap and to minimize the amount of time in which there is only a single source sounding.

@@

		The distance metric cuts the target and solution into successive frames that are 4,000 samples in length, which is approximately 90 milliseconds at a sampling rate of 44.1 kHz. The spectral distance, as defined in Eqn. \ref{eqn:distance}, is calculated between corresponding frames of the target and solution. The spectral distance metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization, and used in \cite{Cella2020b} to compare accuracies of orchestrations. The equation takes in the magnitude spectrums of the FFTs of the target $x$ and of the solution $\tilde{x}$. Then for each bin $k$ of these spectrums, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways. For our purposes, we used $\lambda_1 = 0.5$ and $\lambda_2 = 10$, which penalizes a solution that overshoots the harmonic energy of the target.
